A Large-Scale Study of the Use of Eval in R

### 2020-08-27 inst/paper/main.tex
Updated 3

The pipeline begins with downloading and installing open source R packages from
CRAN for the corpus along with their dependencies. The Kaggle programs are
downloaded from \href{http://www.kaggle.com}{Kaggle} separately by a crawler.
Next, code size and coverage metrics from the installed packages are extracted
using the \href{ https://github.com/r-lib/covr}{\covr} package. This is followed
by extraction of runnable programs from R packages: tests, examples and
vignettes. The extracted programs are then run through \emph{evil} (\emph{Ev}al
\emph{I}nspection \emph{L}ibrary), a dynamic analyzer that collects information
about \eval calls from program runs. This dynamic analyzer builds upon our
dynamic analysis framework, \instrumentr which is another R package that enables
us to write our dynamic analysis logic in R. It internally uses a modified R
interpreter, \rdyntrace~\cite{oopsla19a}, that exposes hooks from within the
interpreter implementation for events of interest. \instrumentr serves as an
intermediary between \rdyntrace and \evil, it intercepts the hooks exposed by
\rdyntrace and attaches R functions exported by \evil as callbacks. The \evil
callbacks execute on corresponding interpreter events. All steps of this
pipeline are parallelized. To schedule and parallelize extraction and analysis
of programs, we use our homegrown library \runr. Furthermore, \runr gracefully
handles and reports failures across large-scale program runs which greatly aids
debugging of the analysis pipeline. The data extracted by \evil from each
program is concatenated, cleaned and summarized in the post-processing phase by
custom R scripts. Finally, the summarized data is analyzed in RMarkdown
notebooks to gather insights. Apart from the figures, the data points included
in the paper are also generated by RMarkdown notebooks as latex macros.

>>>>

The pipeline begins with downloading and installing open source R packages from
CRAN for the corpus along with their dependencies. The Kaggle programs are
downloaded from \href{http://www.kaggle.com}{Kaggle} separately by a crawler.
Next, code size and coverage metrics from the installed packages are extracted
using the \href{ https://github.com/r-lib/covr}{\covr} package. This is followed
by extraction of runnable programs from R packages: tests, examples and
vignettes as well as from Kaggle. The code of each extracted program is wrapped
into a call to dynamic analyzer \emph{evil} (\emph{Ev}al \emph{I}nspection
\emph{L}ibrary) that collect eval usage. The reason for this is that we only
want to record eval usage for the extracted code. Without this, the data would
include eval calls from the unit testing frameworks as well as from
bootstrapping R virtual machine itself. To avoid any interference, each program
is run in its own R instance. The \emph{evil} framework implemented as R package
in 2K lines of R and 400 lines of C++ code.

The dynamic analyzer builds upon our dynamic analysis framework, \instrumentr
that we have implemented to enable us to write dynamic analysis logic in R. It
is an R package implemented in 2.5K lines of R and 6K lines of C++ code. It
internally uses a modified R interpreter, \rdyntrace~\cite{oopsla19a}, that
exposes hooks from within the interpreter implementation for events of interest.
\instrumentr serves as an intermediary between \rdyntrace and \evil, it
intercepts the hooks exposed by \rdyntrace and attaches R functions exported by
\evil as callbacks. The \evil callbacks execute on corresponding interpreter
events.

All steps of this pipeline are parallelized using GNU
parallel~\cite{GNUparallel} and orchestrated by GNU make. To schedule and
parallelize extraction and analysis of programs, we use our homegrown library
\runr. Furthermore, \runr gracefully handles and reports failures across
large-scale program runs which greatly aids debugging of the analysis pipeline.
The data extracted by \evil from each program is concatenated, cleaned and
summarized in the post-processing phase by custom R scripts. Finally, the
summarized data is analyzed in RMarkdown notebooks to gather insights. Apart
from the figures, the data points included in the paper are also generated by
RMarkdown notebooks as latex macros.

All runs are done on a single server Intel Xeon 6140, 2.30GHz with 72 cores and
256GB of RAM.
